Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Proof-of-Concept V}}

### 2014-05-12 Paper.tex
PoC-5 Genesis block updates.

\begin{tabular*}{\columnwidth}[h]{rlrrl}
\toprule
\multicolumn{5}{c}{\textbf{40s: Block Information}} \vspace{5pt} \\
\textbf{Value} & \textbf{Mnemonic} & $\delta$ & $\alpha$ & \textbf{Description} \vspace{5pt} \\
0x40 & {\small PREVHASH} & 0 & 1 & Get hash of most recent complete block. \\
&&&& $\boldsymbol{\mu}'_\mathbf{s}[0] \equiv {I_H}_p$ \\
&&&& $I_{H_p}$ is the previous block's hash. \\
\midrule
0x41 & {\small COINBASE} & 0 & 1 & Get the block's coinbase address. \\
&&&& $\boldsymbol{\mu}'_\mathbf{s}[0] \equiv {I_H}_b$ \\
\midrule
0x42 & {\small TIMESTAMP} & 0 & 1 & Get the block's timestamp. \\
&&&& $\boldsymbol{\mu}'_\mathbf{s}[0] \equiv {I_H}_t$ \\
\midrule
0x43 & {\small NUMBER} & 0 & 1 & Get the block's number. \\
&&&& $\boldsymbol{\mu}'_\mathbf{s}[0] \equiv {I_H}_i$ \\
\midrule
0x44 & {\small DIFFICULTY} & 0 & 1 & Get the block's difficulty. \\
&&&& $\boldsymbol{\mu}'_\mathbf{s}[0] \equiv {I_H}_d$ \\
\midrule
0x45 & {\small GASLIMIT} & 0 & 1 & Get the block's gas limit. \\
&&&& $\boldsymbol{\mu}'_\mathbf{s}[0] \equiv {I_H}_l$ \\
&&&& Presently, the gas limit is hard-coded in the protocol. \\
\bottomrule
\end{tabular*}

@@

The genesis block is 9 items, and is specified thus:
\begin{equation}
\big( \big( 0_{256}, \mathtt{\tiny SHA3}\big(\mathtt{\tiny RLP}\big( () \big)\big), 0_{160}, 0_{256}, 0_{256}, 2^{22}, 0, (), \mathtt{\tiny SHA3}\big( (42) \big) \big), (), () \big)
\end{equation}

@@

The proof-of-concept series include a development premine, making the state root hash some value other than $0_{256}$. The latest documentation should be consulted for the value of the state root.

>>>>

\begin{tabular*}{\columnwidth}[h]{rlrrl}
\toprule
\multicolumn{5}{c}{\textbf{40s: Block Information}} \vspace{5pt} \\
\textbf{Value} & \textbf{Mnemonic} & $\delta$ & $\alpha$ & \textbf{Description} \vspace{5pt} \\
0x40 & {\small PREVHASH} & 0 & 1 & Get hash of most recent complete block. \\
&&&& $\boldsymbol{\mu}'_\mathbf{s}[0] \equiv {I_H}_p$ \\
&&&& $I_{H_p}$ is the previous block's hash. \\
\midrule
0x41 & {\small COINBASE} & 0 & 1 & Get the block's coinbase address. \\
&&&& $\boldsymbol{\mu}'_\mathbf{s}[0] \equiv {I_H}_b$ \\
\midrule
0x42 & {\small TIMESTAMP} & 0 & 1 & Get the block's timestamp. \\
&&&& $\boldsymbol{\mu}'_\mathbf{s}[0] \equiv {I_H}_t$ \\
\midrule
0x43 & {\small NUMBER} & 0 & 1 & Get the block's number. \\
&&&& $\boldsymbol{\mu}'_\mathbf{s}[0] \equiv {I_H}_i$ \\
\midrule
0x44 & {\small DIFFICULTY} & 0 & 1 & Get the block's difficulty. \\
&&&& $\boldsymbol{\mu}'_\mathbf{s}[0] \equiv {I_H}_d$ \\
\midrule
0x45 & {\small GASLIMIT} & 0 & 1 & Get the block's gas limit. \\
&&&& $\boldsymbol{\mu}'_\mathbf{s}[0] \equiv {I_H}_l$ \\
\bottomrule
\end{tabular*}

@@

The genesis block is 13 items, and is specified thus:
\begin{equation}
\big( \big( 0_{256}, \mathtt{\tiny SHA3}\big(\mathtt{\tiny RLP}\big( () \big)\big), 0_{160}, stateRoot, 0_{256}, 2^{22}, 0, 0, 1000000, 0, 0, (), \mathtt{\tiny SHA3}\big( (42) \big) \big), (), () \big)
\end{equation}

@@

The proof-of-concept series include a development premine, making the state root hash some value $stateRoot$. The latest documentation should be consulted for the value of the state root.
